Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-09-28 RegReport/paper.tex
changing tenses in abstract

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we ask whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination}: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we will ask 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. We predict an association of pre-crastination with inefficient search strategies. Personality inventories will also be administered to identify stable characteristics associated with these strategies. 
\end{abstract}

\begin{fmtext}

Human behaviour in visual search tasks is characterised by large individual differences. While both optimal \cite{najemnik-geisler2008,hoppe-rothkopf2019} and stochastic \cite{clarke2016} strategies have been proposed, 
\end{fmtext}
\maketitle
experiments show that different observers utilise different strategies \cite{nowakowska2017,irons-leber2016}, with some approximating the optimal search strategy, others behaving randomly, and others still, making use of a `counter-optimal' strategy. The challenge for a complete understanding of visual search is to identify the source(s) of these individual differences.

>>>>

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we \textcolor{red}{asked} whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination}: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we \textcolor{red}{asked} 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. We \textcolor{red}{predicted} an association of pre-crastination with inefficient search strategies. Personality inventories will also be administered to identify stable characteristics associated with these strategies. \textcolor{red}{We found no evidence of an association between search strategy, pre-crastination, or any of the personality measures collected.}
\end{abstract}

\begin{fmtext}
\end{fmtext}
\maketitle

Human behaviour in visual search tasks is characterised by large individual differences. While both optimal \cite{najemnik-geisler2008,hoppe-rothkopf2019} and stochastic \cite{clarke2016} strategies have been proposed,

experiments show that different observers utilise different strategies \cite{nowakowska2017,irons-leber2016}, with some approximating the optimal search strategy, others behaving randomly, and others still, making use of a `counter-optimal' strategy. The challenge for a complete understanding of visual search is to identify the source(s) of these individual differences.
